\begin{recipe}[
    preparationtime = 30 minutes,
    bakingtime = 2\nicefrac{1}{2} - 3 hours,
    bakingtemperature = {\unit[250]{\farenheit}},
  ]{Brown Bread}
\ingredients{
2 cups & buttermilk \\
\nicefrac{3}{4} cup & dark molasses \\
1 cup & raisins \\
1 cup & whole wheat flour \\
1 cup & rye flour\\
1 cup & yellow cornmeal \\
\nicefrac{3}{4} tsp & baking soda \\
\nicefrac{1}{2} tsp & salt \\
}
\equipment{
3 & 20oz food cans (clean, greased), or \\
4 & 16oz food cans (clean, greased), or \\
4 & 16oz food cans (clean, greased), or \\
2 & mini loaf pans, greased \\
 & aluminum foil \\
 & dutch oven or, \\
 & roasting pan \\
 & mixing bowl \\
}

\preparation { 
% 
\step In mixing bowl, blend buttermilk and molasses. Stir in raisins.
% 
\step Thoroughly stir together whole wheat flour, rye flour, cornmeal,
soda, and salt
%
\step Stir flour mixture into into buttermilk mixture until
  blended.
% 
\step Divide batter amonst food cans or loaf pans. Cover tightly with
foil; place on rack set in large Dutch oven, a large pan or pot, or a
roasting pan. 
%
\step Pour in boiling water to a depth of one inch. Cover and simmer
over low heat, or bake in the oven, steaming bread for 2 1⁄2 to 3
hours or ‘till done and adding more boiling water as needed.
%
\step Remove bread from cans and cool on rack.
}
\end{recipe}

\begin{recipe}[
    preparationtime = 15 minutes,
    bakingtime = 12-15 minutes,
    bakingtemperature = {\unit[450]{\farenheit}},
  ]{Buttermilk Biscuits}
\ingredients{
\nicefrac{1}{4} cup & shortening \\
\nicefrac{3}{4} cup & buttermilk \\
2 cups & flour \\
}
\equipment{
1 & 9'' pie plate, greased \\
 & mixing bowl
}

\preparation {
%
\step In mixing bowl, cut shortening into flour until it has the
consistency of coarse crumbs.
%
\step Make a well in the center, add milk.
%
\step Stir quickly with fork just till dough follows fork around
bowl. 
%
\step Divide in eighths, forming each into a ball.
%
\step Place in greased 9" pie plate.  Flatten tops.
%
\step Bake at \unit[450]{\farenheit} for 12-15 minutes or until golden
brown.
}
\end{recipe}

