\begin{recipe}[
    preparationtime = 30 minutes,
  ]{Black Bottom Pie}
\ingredients{
1 & 9 inch baked pie shell \\
1 envelope & unflavored gelatin \\
\nicefrac{1}{4} cup & cold water \\ 
1 cup & sugar \\
\nicefrac{1}{2} tsp & salt \\
\nicefrac{1}{4} cup & corn starch \\
2 cups & milk \\
4 & egg yolks, well beaten \\
1 cup (6 oz) & chocolate chips \\
1 tsp & vanilla \\
 & egg whites \\
\nicefrac{1}{4} tsp & cream of tartar \\
\nicefrac{1}{2} tsp & rum extract \\
 & chocolate curls \\
 & or shavings (optional) \\
}
\equipment{
Mixer \\
Sauce pan \\
}

\preparation {
%
\step Combine gelatin and cold water in a custard cup. Place the cup
in a pan of simmering water to dissolve gelatin.
%
\step Mix \nicefrac{1}{2} cup of the sugar with the salt and corn
starch in a sauce pan. Gradually add milk and cook over low heat,
stirring constantly, until thickened. Slowly beat hot mixture into egg
yolks. Return to saucepan, cook, stirring constantly, for two
minutes. Remove from heat and blend 1\nicefrac{1}{2} cups of this
custart mixture with chocolate chips. Add vanilla and pour in to pie
shell. Chill.
%
\step Combine dissolved gelatin with remaining custard. Add rum
extract and set aside.
%
\step Beat egg whites with cream of tartar until frothy. Gradually add
remainder of sugar, and continue to beat until stiff peaks form. Fold
gelatin-custard mixture into beaten egg whites. Chill 15 minutes or
until partially set. Spoon over chocolate custard in pie shell. Chill.
%
\step Garnish and serve.
}
\hint
    {%
      {\bf Variation:} substitute mint for rum.
    }
\end{recipe}
